\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper}
\geometry{margin=1in}

\title{MSU Minutes}
\date{March 9, 2020}

\begin{document}
\maketitle

Meeting duration: 10:48 - 11:01

\section*{Attendence}
\begin{itemize}
\item \textit{Executives.} Sebastian Mora, Maksym Neyra-Nesterenko, Aisosa Efemwonkieke, Paymon Jalali.
\item \textit{Students.} Justin Yan, Brandon Zhu, Paymon Jalali, Nosa Efemwonkieke, Gemk Wong, Jacques van Wyk.
\end{itemize}

\subsection*{Discussion}
\begin{itemize}
\item \textbf{Vote passes unanimously in favour to} allocate \$200 from core to the SUS Winter Formal 2020.
\item Club Ilia dinner event with MSU and SASSA on April 3; motion for a grant \textit{(see below)}.
\end{itemize}

\subsection*{Upcoming events}
\begin{itemize}
\item End-of-semester study session on April 7; motion for funding food \textit{(see below)}.
\end{itemize}

\subsection*{Motions}
\begin{itemize}
\item Sebastian Mora motions to reimburse Brandon Zhu \$150 from core for custom T-shirt production, Paymon Jalali seconds, motion passes.
\item Paymon Jalali motions to reimburse Sebastian Mora \$30 from core for snacks and cleaning supplies, Aisosa Efemwonkieke seconds, motion passes.
\item Paymon Jalali motions \$130 from core to cover extra charges for purchasing a water dispenser (with Best Buy gift cards), Sebastian Mora seconds, motion passes.
\item Sebastian Mora motions \$100 from core for extra water dispenser supplies (coffee, food, ramen, etc.), Paymon Jalali seconds, motion passes.
\item Sebastian Mora motions \$100 from core to purchase printer toner, Aisosa Efemwonkieke seconds, motion passes.
\item Sebastian Mora motions \$50 from core for a \$500 grant (for Club Ilia event), Aisosa Efemwonkieke seconds, motion passes.
\item Paymon Jalali motions \$200 from core to purchase food for MSU study session on April 7, Sebastian Mora seconds, motion passes.
\end{itemize}

\section*{Accounts}
Trust account: \$1107.50 \\
Core funding: \$1490.47 \\

\end{document}