\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper}
\geometry{margin=1in}

\title{MSU Minutes}
\date{January 27, 2020}

\begin{document}
\maketitle

Meeting duration: 10:45 - 11:13

\section*{Attendence}
\begin{itemize}
\item \textit{Executives.} Sebastian Mora, Maksym Neyra-Nesterenko, Aisosa Efemwonkieke, Paymon Jalali, Brendan Kelly.
\item \textit{Students.} Aiya Bowman, Brandon Zhu, Gracee Zy, Justin Yan, Jamie Lo, Jacques van Wyk, Jessica Sairi, Gerrik Wong, Paige Nicholson.
  
\end{itemize}

\subsection*{Upcoming events}
\begin{itemize}
\item Applied mathematics seminar on Friday at 3:30 to 4:30.
\item Third batch of MSU hoodies coming soon.
\end{itemize}

\subsection*{Discussion}
\begin{itemize}
\item Custom T-shirts being put together and provided by Brandon, \textit{see motion below}.
\item \textbf{Majority vote in favour to} spend Best Buy gift cards (won from Science Trivia Night) on a coffee machine.
\item \textbf{Majority voted in opposition to} Brandon is selling face masks branded by the MSU.
\end{itemize}

\subsection*{Motions}
\begin{itemize}
\item Aisosa Efemwonkieke motions to reimburse Sebastian Mora \$10 from core for Timbits, Brendan Kelly seconds, motion passes.
\item Sebastian Mora motions to pay \$150 from core to pay for 30 patches \textit{to Brandon Zhu} to put together T-shirts, Paymon Jalali seconds, motion passes.
\item Aisosa Efemwonkieke motions to reimburse Paymon Jalali \$20 from core if Best Buy gift card spending exceeds our threshold, Sebastian Mora seconds, motion passes.
\item Paymon Jalali (on Mitchell Gale's behalf) motions \$160.76 to be paid out from Grant 1109 (appetizer party) to be made out to Sebastian Mora, Aisosa Efemwonkieke seconds, motion passes.
\item Paymon Jalali (on Mitchell Gale's behalf) motions \$100.00 from core to reimburse Sebastian Mora for End-of-Semester Social, Aisosa Efemwonkieke seconds, motion passes.
\end{itemize}

\section*{Accounts}

Trust account: \$591.50 \\
Core funding: \$1521.29 \\

\end{document}